---
title: "convert base plot to grob object"
author: "Guangchuang Yu\\

        School of Public Health, The University of Hong Kong"
date: "`r Sys.Date()`"
output:
  prettydoc::html_pretty:
    toc: true
    theme: cayman
    highlight: github
  pdf_document:
    toc: true
vignette: >
  %\VignetteIndexEntry{base2grob introduction}
  %\VignetteEngine{knitr::rmarkdown}
  %\usepackage[utf8]{inputenc}
---

```{r style, echo=FALSE, results="asis", message=FALSE}
knitr::opts_chunk$set(tidy = FALSE,
		   message = FALSE)
```


```{r echo=FALSE, results="hide", message=FALSE}
library("ggplot2")
library("cowplot")
library("grid")
library("base2grob")
```




```{r warning=FALSE}
library("grid")
library("base2grob")

p1 <- base2grob(~barplot(1:10))
p2 <- base2grob(expression(plot(rnorm(10))))
p3 <- base2grob(~pie(1:5))
p4 <- base2grob(function() plot(sin))
```


`base2grob` function accepts base plot function call as `expression` or
`formula`, or a function that plots to an R graphics device. It will convert the plot to `grob` object, so that it can be
compatible with `grid` system and related packages.

## grid

We can now use `grid.draw` to plot `p1` and `p2`, and use `pushViewport` to
embed plot inside another plot.


```{r fig.width=7, fig.height=7}
grid.newpage()
grid.draw(p1)
vp = viewport(x=.35, y=.75, width=.35, height=.3)
pushViewport(vp)
grid.draw(p2)
upViewport()
```

## ggsave

The object is compatible with `ggplot2::ggsave()` and can be exported to
file using `ggsave()`:

```{r}
library(ggplot2)

f <- tempfile(fileext = ".pdf")
f
ggsave(p1, filename = f)
file.info(f)$size

## we can even directly using formula or expression of base plot command inside ggsave
ggsave(~pie(1:3), filename = f)
file.info(f)$size

## even function is supported
ggsave(function() plot(sqrt), filename = f)
file.info(f)$size
```

## plot_grid

We can now use `cowplot::plot_grid()` to align base plots.

```{r fig.width=10, fig.height=6}
library(cowplot)
p5 <- base2grob(~image(volcano))
p6 <- qplot(rnorm(10), rnorm(10)) + theme_grey()
plot_grid(p1, p2, p3, p4, p5, p6, ncol=3, labels=LETTERS[1:6])
```
